Competing Bandits: \\ The Perils of Exploration under Competition

### 2018-11-06 paper/content/inverted_u.tex
Revision in "welfare".

\asedit{We assume that both firms play their respective equilibrium strategies for the corresponding competition level. As discussed previously, these are:}
\ascomment{Guy, pls fill in, and refer to the corresponding findings.}

Figure \ref{eq_regret} displays the \swedit{market regret (average
  over multiple runs)} under different levels of competition.
Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. However, this was expected from the fact that the incumbent is incentivized to play \TS. The welfare in the temporary monopoly case is close to the welfare to having a single firm playing
\TS. \gaedit{We also observe that monopoly and duopoly achieve similar welfare, with monopoly being marginally better than duopoly.}

\begin{finding}
\textit{ In equilibrium, consumer welfare is highest under temporary monopoly. Monopoly and duopoly achieve similar welfare with monopoly leading to marginally better welfare than duopoly.
}
\end{finding}

\gaedit{The result that monopoly leads to marginally better welfare than duopoly is surprising since, in equilibrium, all firms play \DG in both settings. One might conjecture that the welfare should increase with the number of firms playing \DG since more \DG runs
  should result in faster concentration on playing the better arms. In
  particular, more firms playing \DG should result in faster
  discovery of a better arm, and the firm with such discovery would be
  able to attract more consumers and increase market welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and EEOG as we increase \#firms playing \DG}
\label{many_firm_welfare}
\end{figure}

\begin{finding}
\textit{When all firms in the market deploy \DG, welfare is weakly decreasing as the number of firms in the market decreases.}
\end{finding}
\swedit{To study this phenomenon further, we go beyond the two-firm
  setting and simulate the game an increasing number of firms playing
  \DG.} Figure \ref{many_firm_welfare} reports the average welfare
across these simulations. Welfare not only does not get better,
\textit{but is weakly worse} as we increase the number of
firms. Correspondingly, we track the average \Eeog in each of the
simulations and notice that it is \textit{increasing} as the number of
firms increases. As we increase the number of firms, a single
individual firm gets fewer consumers for learning as consumers switch
between firms more often. Additionally, bad luck with rewards or arm
selection is punished even more harshly as we increase the number of
firms. This further strengthens the intuition from our previous
result, which is that learning may be hard under competition since
exploration and mistakes are punished harshly but are necessary for
learning.

>>>>

\asedit{We assume that both firms play their respective equilibrium strategies for the corresponding competition level. As discussed previously, these are: 
\begin{itemize}
\item \DG in the monopoly, 
\item \DG for both firms in duopoly (Finding \ref{find:duopoly}),
\item \TS for the incumbent (Finding \ref{find:temp-monopoly}) and \DG for the entrant in temporary monopoly (Finding \ref{find:temp-monopoly-entrant}).
\end{itemize}
} %%%%%%%

Figure \ref{eq_regret} displays the market regret (averaged
  over multiple runs) under different levels of competition.
Consumers are \textit{better off} in the temporary monopoly case than in
the duopoly case. \asedit{Recall that under temporary monopoly, the incumbent is incentivized to play \TS. Moreover, we find that the welfare is close to that of having a single firm for all agents and running \TS. We also observe that monopoly and duopoly achieve similar welfare.}
%with monopoly being marginally better than duopoly.

\begin{finding}\label{find:welfare}
\textit{In equilibrium, consumer welfare is (a) highest under temporary monopoly, (b) similar for monopoly and duopoly.
%monopoly being marginally better leading to marginally better welfare than duopoly.
}
\end{finding}

\asedit{Finding~\ref{find:welfare}(b) is interesting because, in equilibrium, both firms play \DG in both settings, and one might conjecture that the welfare should increase with the number of firms playing \DG. Indeed, one run of \DG may get stuck on a bad arm. However, two firms independently playing \DG are less likely to get stuck simultaneously. If one firm gets stuck and the other does not, then the latter should attract most agents, leading to improved welfare.}
\begin{figure}
\includegraphics[scale=0.3]{figures/eeog_vs_num_ht}
\includegraphics[scale=0.3]{figures/ht_many_firm_welfare}\\
\caption{Average welfare and EEOG as we increase \#firms playing \DG}
\label{many_firm_welfare}
\end{figure}

To study this phenomenon further, we go beyond the duopoly setting to more than two firms playing \DG (and starting at the same time). Figure \ref{many_firm_welfare} reports the average welfare
across these simulations. Welfare not only does not get better, \textit{but is weakly worse} as we increase the number of firms.

\begin{finding}
\textit{When all firms deploy \DG, and start at the same time, welfare is weakly decreasing as the number of firms decreases.}
\end{finding}

We track the average \Eeog in each of the
simulations and notice that it is \textit{increasing} as the number of
firms increases. As we increase the number of firms, a single
individual firm gets fewer consumers for learning as consumers switch
between firms more often. Additionally, bad luck with rewards or arm
selection is punished even more harshly as we increase the number of
firms. This further strengthens the intuition from our previous
result, which is that learning may be hard under competition since
exploration and mistakes are punished harshly but are necessary for
learning.
